### 2014-10-30 motivation.tex
The placement of ref to Fig. 3 changed

\name helps facilitate the mapping of operations to appropriate consistency
levels by letting the programmer declare application-level consistency
constraints as \emph{contracts} that axiomatically specify the set of allowed
executions involving this operation.  In the case of the bank account example,
any execution that does not exhibit the anomalies described in the previous
section is a \emph{well-formed} execution on the bank account object.  By
specifying the set of legal executions for each data type in terms of a trace
of operation invocations on that type, \name\ ensures that all executions over
that type are well-formed.

@@

Our specification language (Fig~\ref{fig:contract-lang}) provides
operators to compose relations. Thus, the syntax $(R_1 \cap R_2)(a,b)$
is equivalent to $R_1(a,b) \wedge R_2(a,b)$. The last line of the
above contract says that if a \cf{deposit} or a \cf{withdraw}
operation precedes a \cf{getBalance} operation in session order, and
is applied on the same object as the \cf{getBalance} operation, then
it must be the case that the \cf{getBalance} operation witnesses the
effects of the preceding operations.

>>>>

\name helps facilitate the mapping of operations to appropriate consistency
levels by letting the programmer declare application-level consistency
constraints as \emph{contracts} (Fig~\ref{fig:contract-lang}) that axiomatically
specify the set of allowed executions involving this operation. In the case of
the bank account example, any execution that does not exhibit the anomalies
described in the previous section is a \emph{well-formed} execution on the bank
account object.  By specifying the set of legal executions for each data type in
terms of a trace of operation invocations on that type, \name\ ensures that all
executions over that type are well-formed.

@@

Our specification language  provides operators to compose relations.
Thus, the syntax $(R_1 \cap R_2)(a,b)$ is equivalent to $R_1(a,b)
\wedge R_2(a,b)$. The last line of the above contract says that if a
\cf{deposit} or a \cf{withdraw} operation precedes a \cf{getBalance}
operation in session order, and is applied on the same object as the
\cf{getBalance} operation, then it must be the case that the
\cf{getBalance} operation witnesses the effects of the preceding
operations.
